Case study validations of automatic bullet matching

### 2018-10-02 index.Rmd
land-to-land comparisons for six bullets from the Hamby set

>>>>

```{r, fig.width=7.5, fig.height=2.8, fig.cap="Examples of land-to-land comparisons from the Hamby-44 set. Along the top are the three bullets from different source with the highest RF scores, along the bottom are the three bullets from same source with the lowest RF score.", fig.subcap=c("Ground truth: different source", "Ground truth: same-source"), fig.align="middle", fig.ncol=1}
ex2 <- h44nest %>% filter(samesource == FALSE & sam_rf >= 0.295)
rfs2 <- ex2$sam_rf
ex2 <- ex2 %>% mutate(
  data = data %>% purrr::map(.f = function(d) {
 #   browser()
    index <- which.max(bulletxtrctr::compute_average_scores(d$land1, d$land2, d$rfscore))
    d$same <- ((d$land2 - d$land1) %% 6)  == index-1

  #   d %>% ggplot(aes(x = land1, y=land2, fill=rfscore)) + 
  #                  geom_tile() +
  #     geom_tile(colour="darkorange", data = d %>% filter(same), size=0.5) +
  #     scale_fill_gradient2(low="darkgrey", high = "darkorange",
  #                      midpoint = 0.5) +
  #     scale_colour_manual(values=c( "darkorange")) +
  # scale_x_discrete("") +
  # scale_y_discrete("")
    d
  })
)
ex2$example <- with(ex2, paste0(bullet1, " vs ", barrel2, "-", bullet2))
ex2 <- unnest(ex2, data)
ex2 %>% 
  ggplot(aes(x = land1, y = land2, fill=rfscore)) + 
  geom_tile() +
  theme_bw() +
  scale_fill_gradient2("RF score", low="darkgrey", high = "darkorange",
                       midpoint = 0.5) +
#  geom_tile(colour="darkgrey", data = ex2 %>% filter(same), size=0.5) +
  facet_grid(.~example) +
  scale_x_discrete("") +
  scale_y_discrete("") +
  annotate(geom="text", x = 0.5, y = 6.75, label=sprintf("SAM RF: %.3f", rfs2), hjust = 0)

ex1 <- h44nest %>% filter(samesource == TRUE & sam_rf < 0.4)
rfs <- ex1$sam_rf
ex1 <- ex1 %>% mutate(
  data = data %>% purrr::map(.f = function(d) {
 #   browser()
    index <- which.max(bulletxtrctr::compute_average_scores(d$land1, d$land2, d$rfscore))
    d$same <- ((d$land2 - d$land1) %% 6)  == index-1

  #   d %>% ggplot(aes(x = land1, y=land2, fill=rfscore)) + 
  #                  geom_tile() +
  #     geom_tile(colour="darkorange", data = d %>% filter(same), size=0.5) +
  #     scale_fill_gradient2(low="darkgrey", high = "darkorange",
  #                      midpoint = 0.5) +
  #     scale_colour_manual(values=c( "darkorange")) +
  # scale_x_discrete("") +
  # scale_y_discrete("")
    d
  })
)
ex1$example <- with(ex1, paste0(bullet1, " vs ", barrel2, "-", bullet2))
ex1 <- unnest(ex1, data)
ex1 %>% 
  ggplot(aes(x = land1, y = land2, fill=rfscore)) + 
  geom_tile() +
  theme_bw() +
  scale_fill_gradient2("RF score", low="darkgrey", high = "darkorange",
                       midpoint = 0.5) +
  geom_tile(colour="darkorange", data = ex1 %>% filter(same), size=0.5) +
  facet_grid(.~example) +
  scale_x_discrete("") +
  scale_y_discrete("") +
  annotate(geom="text", x = 0.5, y = 6.75, label=sprintf("SAM RF: %.3f", rfs), hjust = 0)
```
